---
title: "CourseProject"
author: "Gustavo Alurralde"
date: "25 de diciembre de 2015"
output: html_document
---

#Course Project

##Introduction

This document tries to answer the points of the course project of the Practical Machine Learning Course.

##Preparation

First I will load the data and the caret package.

```{r, echo=FALSE}
  load("data.RData")
```

```{r, results='hide', error=FALSE, warning=FALSE, message=FALSE}
  library(caret)
  datos <- read.csv(file = "./pml-training.csv")
```

Second I will cut the values that present NA values as the attributes: X, user_name, raw_timestamp_part_1, 
raw_timestamp_part_2, cvtd_timestamp, new_window and num_window that i found dispensable.

```{r}
  ndatos <- datos[,c(8,9,10,11,37,38,39,40,41,42,43,44,45,46,47,48,49,60,61,62,63,64,65,66,67,68,84,85,86,102,113,114,115,
                     116,117,118,119,120,121,122,123,124,140,151,152,153,154,155,156,157,158,159,160)]
```

After that, I set the seed for reproducibility purposes and split the data. 90% of the data for training and 10% for testing

```{r}
  set.seed(1992)
  trainRows <- createDataPartition(y = ndatos$classe, p = 0.90, list = FALSE )
  train <- ndatos[trainRows,]
  test <- ndatos[-trainRows,]
```

##Model
After that I tried to fit a model by random forest but my PC worked for 2 hours and didn't finish, so i started over 
but tried with Stochastic Gradient Boosting.
  
```{r, eval=FALSE}
  fit <- train( classe ~ . , data = train , method="gbm" , verbose = FALSE )
```

In order to see how does it perform, I will predict the values of the training set
```{r, results='hide', error=FALSE, warning=FALSE, message=FALSE}
  pred <- predict(object = fit,newdata = train)
```
```{r}
  table(train$classe,pred)
```

As can be seen, the fit is very good. In order to be more specific. I can calculate the error percentaje

```{r}
  pct <- count( train$classe == pred )
  pct[pct$x=="FALSE","freq"] / nrow(train)
```

The fit's error rate is very low. 

##Test
I will proceed to test it in the other 10% of the data.

```{r}
  testpred <- predict(object = fit, newdata = test)
  table(test$classe, testpred)
  
  pcttest <- count( test$classe == testpred)
  pct[pcttest$x=="FALSE","freq"] / nrow(test)
```


##Answer
Finally, predict the final test data

```{r}
  Finaltest <- read.csv(file = "./pml-testing.csv")

  finaldatos <- Finaltest[,c(8,9,10,11,37,38,39,40,41,42,43,44,45,46,47,48,49,60,61,62,63,64,65,66,67,68,84,85,86,102,113,114,115,
                     116,117,118,119,120,121,122,123,124,140,151,152,153,154,155,156,157,158,159,160)]
  
  finalpred <- predict( object = fit, newdata = finaldatos)
```

And generate the files

```{r, eval=FALSE}
  pml_write_files = function(x){
    n = length(x)
    for(i in 1:n){
      filename = paste0("problem_id_",i,".txt")
      write.table(x[i],file=filename,quote=FALSE,row.names=FALSE,col.names=FALSE)
    }
  }
  
  pml_write_files(finalpred)
```
  
